Embedded Scalars, Preferred Readings \& Prosody: {A}n Experimental Revisit

### 2015-10-17 text/paper/revision_02/paper.tex
K2 rev edits
sec 4.4 edits

  \subfloat[test][Results \es-condition]{
    \label{fig:CS-Results-es}
    \includegraphics[width=5.5cm]{pictures/paper/Chemla_Spector_2010_Results_GE.png}
  }  
   \end{minipage}
        \caption{Example trial and results of
          \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
          (\citeyear{ChemlaSpector2010:Experimental-Ev}) study.}
\end{figure}

@@

Summing up, three experimental studies have presented diverging pieces
of evidence. % \citet{GeurtsPouscoulous2009:Embedded-Implic} did not
% observe any truth value-judgments that would indicate local readings
% in a picture verification task and thus conclude that these readings
% are unavailable. \citet{CliftonDube2010:Embedded-Implic} and
% \citet{ChemlaSpector2010:Experimental-Ev} employed different designs
% intended to be sensitive enough to reveal local readings. Both studies
% found putative evidence in support of local readings.
Differences in results are likely due to differences in experimental
design, in particular due to (i) the type of elicited judgement and
(ii) the possibility of conflating pictorial effects.

@@

We are generally sympathetic towards
\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
reinterpretation of the data, but note, as
\citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
typicality-based explanation does not extend to \es-sentences in an
obvious way. Moreover, typicality itself is not a satisfactory
primitive in a putative explanation of the use of quantifiers, but
rather something that needs explanation itself \citep[c.f.][for
critical reflection on typicality-based
explanations]{Cummins2014:Typicality-made}. Indeed, it is possible to
explain typicality judgements as the outcome of Gricean speaker
preferences for informative descriptions, just like those that
rationalize quantity implicatures \citep{Franke2014:Typical-use-of-}.
For these reasons, we believe that typicality and other pictorial
effects need to be taken seriously in the experimental design, but do
not necessarily give a satisfactory account of the observed variation
all by themselves.

\paragraph{Upshot.} Taken together, we would ideally like a design
that evokes categorical truth value judgments in a way that is as
independent as possible of potentially conflating properties of the
pictorial material and that is nonetheless sensitive enough to detect
local readings even if they are dispreferred. The sensitivity to
dispreferred readings should be controlled for. On top of this, it
would be desirable to obtain further information about the relative
preferences among all putative readings, so as to be able to decide
between theoretical positions, as outlined in
Section~\ref{sec:theories-predictions}. % Neither of the previous
% studies gives us that, either because they simply have not
% investigated all the relevant comparisons
% (\citet{GeurtsPouscoulous2009:Embedded-Implic},
% \citet{CliftonDube2010:Embedded-Implic}), or because they cannot
% safely derive the required information for danger of conflating
% preferences for readings with preferences for pictures
% (\citet{ChemlaSpector2010:Experimental-Ev}).

Finally, we need to control for ``silent prosody.'' Several studies
suggest that numerous factors might influence accent placement and
prosodic phrasing even while reading, amongst them default
accentuation, constituent length, rhythmic phenomena, and individual
variation
\citep[e.g.][]{Bader98,Fodor98,Steinhauer01,Fodor02,Augurzky08,BreenWatson2011:Intonational-ph,Kentner12}. If
we adopt the prosodic markedness hypothesis described in
Section~\ref{sec:inton-mark-hypoth}, as many traditionalists do, we
predict that the availability of a local reading hinges on the
realization of contrastive stress on the scalar item
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
But if prosody can have this role, it is necessary to control for
silent accent placement. Ideally, therefore, we should present
sentences auditorily and systematically manipulate contrastive stress.

@@

\paragraph{General Idea.} In order to test the availability and
preferences of different readings of \as- and \es-sentences in German,
we were looking for a way to unambiguously map responses from a
picture-verification task to specific readings. We were particularly
interested in the question whether local readings would be observed at
all, and whether their presence or absence would be modulated by a
contrastive accent on the scalar item. Moreover, we were interested in
obtaining information about the relative preferences of the different
readings. In addition, we wanted to minimize potential picture
typicality effects. To achieve this (see
Section~\ref{sec:discussion-1} for discussion), we used an
\emph{incremental verification task} (\acro{ivt}), which is a
modified version of picture verification
\citep[see][]{Conroy2008}. The general idea is that subjects are
requested to judge sentence material with respect to pictures that do
not necessarily contain all the information relevant for judging a
certain reading true or false. In that case, participants can demand
that more information be revealed. Participants are instructed to make
a truth-value judgment as soon as they are able to. When they do, the
trial ends.

>>>>

  \subfloat[test][Results \es-condition]{
    \label{fig:CS-Results-es}
    \includegraphics[width=5.5cm]{pictures/paper/Chemla_Spector_2010_Results_GE.png}
  }  
   \end{minipage}
   \caption{Example trial and results of \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
     (\citeyear{ChemlaSpector2010:Experimental-Ev}) study. Test sentences for pictures like on
     the left where: ``Every letter is connected to some of its circles.''}
\end{figure}

@@

Summing up, three experimental studies have presented diverging pieces
of evidence. % \citet{GeurtsPouscoulous2009:Embedded-Implic} did not
% observe any truth value-judgments that would indicate local readings
% in a picture verification task and thus conclude that these readings
% are unavailable. \citet{CliftonDube2010:Embedded-Implic} and
% \citet{ChemlaSpector2010:Experimental-Ev} employed different designs
% intended to be sensitive enough to reveal local readings. Both studies
% found putative evidence in support of local readings.
Differences in results might be due to differences in experimental design, in particular due to
the type of elicited judgement and the possibility of conflating pictorial effects. Also, we
should reflect on the effects of ``silent prosody.''

@@

We are generally sympathetic towards \citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative
line of reinterpretation of the data, but note, as \citet{ChemlaSpector2010:Experimental-Ev}
already observed, that his typicality-based explanation does not extend to \es-sentences in an
obvious way. Moreover, typicality itself is not a satisfactory primitive in a putative
explanation of the use of quantifiers, but rather something that needs explanation itself
\citep[c.f.][for critical reflection on typicality-based
explanations]{Cummins2014:Typicality-made}. Indeed, it is possible to explain typicality
judgements as the outcome of Gricean speaker preferences for informative descriptions, just
like those that rationalize quantity implicatures \citep{Franke2014:Typical-use-of-}.  For
these reasons, we believe that typicality and other pictorial effects need to be taken
seriously in the experimental design, but do not necessarily give a satisfactory account of the
observed variation all by themselves. In other words, if we take worries about pictorial
effects seriously, we need to reconsider conclusions from previous studies in the light of data
from a task that minimizes pictorial effects as much as possible.

\paragraph{``Silent prosody.''} Several studies suggest that numerous factors might influence
accent placement and prosodic phrasing even while reading, amongst them default accentuation,
constituent length, rhythmic phenomena, and individual variation
\citep[e.g.][]{Bader98,Fodor98,Steinhauer01,Fodor02,Augurzky08,BreenWatson2011:Intonational-ph,Kentner12}. If
we adopt the prosodic markedness hypothesis described in Section~\ref{sec:inton-mark-hypoth},
as many traditionalists do, we predict that the availability of a local reading hinges on the
realization of contrastive stress on the scalar item
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
But if prosody can have this role, it is necessary to control for silent accent
placement. Ideally, therefore, we should present sentences auditorily and systematically
manipulate contrastive stress.

\paragraph{Upshot.} This leaves us with the following desiderata. (i) In order to test the
availability and preferences of different readings of \as- and \es-sentences, we need a way to
unambiguously map responses, ideally categorical, to specific readings. (ii) We should try to
avoid issues of ``silent prosody'' and actively explore the role of prosodic markedness. (iii)
We would like to obtain information about the relative preferences of the different readings,
ideally by comparison to some other, ``base-line'' condition. Finally (iv) we want to minimize
potential picture typicality effects.

@@

\paragraph{General Idea.} To deal with these desiderata, we used an \emph{incremental
  verification task} (\acro{ivt}), which is a modified version of picture verification
\citep[see][]{Conroy2008}. The general idea is that subjects are requested to judge sentence
material with respect to pictures that do not necessarily contain all the information relevant
for judging a certain reading true or false. In that case, participants can demand that more
information be revealed. Participants are instructed to make a truth-value judgment as soon as
they are able to. When they do, the trial ends.
